---
title: "Social Sciences CoP Presentation"
author: "Matthew DeLoia, matthew.deloia@ngc.com"
date: "9/2/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

#load libraries

library (memisc)
library(chron)
library(cluster)
library(corrplot)
library(eRm)
library(foreign)
library(gganimate)
library(ggcorrplot)
library(ggdendro)
library(hms)
library(imputeMissings)
library(lubridate)
library(mclust)
library(plotly)
library(pracma)
library(randomForest)
library(readxl)
library(Rmisc)
library(stringr)
library(tidyverse)
library(tm)
library(wordcloud)
library(wordcloud2)
library(janitor)
library(lavaan)
library(DecisionAnalysis)

likertNum <- function(x){
        case_when(
                x == "Very Accurate" ~ 5,
                x == "Moderately Accurate" ~ 4,
                x == "Neither Accurate Nor Inaccurate" ~ 3,
                x == "Moderately Inaccurate" ~ 2,
                x == "Very Inaccurate" ~ 1
        )
}

likertNum2 <- function(x){
  case_when(
    x == "VERY ACCURATE" ~ 5,
    x == "MODERATELY ACCURATE" ~ 4,
    x == "NEITHER INACC NOR ACCUR" ~ 3,
    x == "MODERATELY INACCURATE" ~ 2,
    x == "VERY INACCURATE" ~ 1
  )
}

#Load and Process Eugene-Springfield dataset
df_ESDemo <- as.data.set(spss.portable.file("demographics.por"), to.data.frame=T)
df_ESDemo <-as.data.frame(df_ESDemo)
df_ES <- as.data.set(spss.portable.file("IPIP2539-1.por"), to.data.frame=T)
df_ES <- as.data.frame(df_ES)
df_ES2 <- df_ES %>% dplyr::select (ID, A1:A99, C1:C9, M1:M9) %>% gather(A1:A99, C1:C9, M1:M9, key=Question, value = Response, na.rm = TRUE)
df_ES2$Response <- toupper(df_ES2$Response)
df_ES3 <- df_ES2 %>% 
  mutate_at(vars(`Response`), likertNum2) %>% 
  spread(key=Question, value=Response) 
df_ES4 <- df_ES %>%  dplyr::select(-(A1:A99),-(C1:C9), -(M1:M9)) %>% left_join(df_ES3, by="ID")
df_ES5 <- df_ESDemo %>% left_join(df_ES4, by="ID")
df_ES5$ID <- as.character(df_ES5$ID)
df_ESscored <- df_ES5 %>% group_by(ID) %>% 
  mutate(Anxiety = (sum(H926,H980, S3, H761, X107 ) ),      
         Social_Astuteness = (sum(H1137, P432, P451, V96, V153)),
         Breadth_of_Interest = (sum(X211, V140, V2, V330, H1265) ), 
         Complexity = (sum(H1276, Q228, H1267, H1284, V256) ), 
         Social_Confidence = (sum(H1110,S29,P364, H1366, H16 ) ), 
         Cooperativeness = (sum(P420,E147,D107,E68, H974)),  
         Empathy = (sum(D19, X253,H173,	D6,Q256) ), 
         Energy_Level = (sum(H54,	H555,H554,Q151,H79) ), 
         Innovation = (sum(H53,	V259,V226, H447,  X225) ),  
         Organization  = (sum(V98,Q163,V261, H258, V12) ), 
         Responsibility = (sum(H152,V303, D10, E80,V170) ), 
         Risk_Taking = (sum(S19,S4, R77, R58, Q126) ), 
         Sociability = (sum(D70,X161, H78, H985, Q238) ), 
         Tolerance = (sum(H148, Q59, X59, D113, X90) ),
         Traditional_Values = (sum(D88, V46, Q44, H296, X76) ) ) %>%
  dplyr::select (ID, SEX, AGE, EMPLOY, Anxiety:Traditional_Values) %>%
  dplyr::rename(Age = AGE, Gender = SEX) %>% na.omit() 
df_ESscored$Gender <- gsub("M", "Male", df_ESscored$Gender )
df_ESscored$Gender <- gsub("F", "Female", df_ESscored$Gender )

#filter to desired comparative population
df_ESscored2 <- df_ESscored  %>%  dplyr::select(ID, Gender, Age, Anxiety:Traditional_Values )  %>% na.omit()
summaryES <- df_ESscored2 %>% gather(Anxiety:Traditional_Values, key=Dimension, value=Score) %>% summarySE(groupvars = "Dimension", measurevar = "Score" )

anxiety <- summaryES %>% filter(Dimension=="Anxiety")
breadth_of_interest <- summaryES %>% filter(Dimension=="Breadth_of_Interest")
complexity <- summaryES %>% filter(Dimension=="Complexity")
cooperativeness <- summaryES %>% filter(Dimension=="Cooperativeness")
empathy <- summaryES %>% filter(Dimension=="Empathy")
energy_level <- summaryES %>% filter(Dimension=="Energy_Level")
innovation <- summaryES %>% filter(Dimension=="Innovation")
organization <- summaryES %>% filter(Dimension=="Organization")
responsibility <- summaryES %>% filter(Dimension=="Responsibility")
risk_taking <- summaryES %>% filter(Dimension=="Risk_Taking")
sociability <- summaryES %>% filter(Dimension=="Sociability")
social_astuteness <- summaryES %>% filter(Dimension=="Social_Astuteness")
social_confidence <- summaryES %>% filter(Dimension=="Social_Confidence")
tolerance <- summaryES %>% filter(Dimension=="Tolerance")
traditional_values <- summaryES %>% filter(Dimension=="Traditional_Values")
responsibility <- summaryES %>% filter(Dimension=="Responsibility")


#load data

df <- read_excel("SocialScienceCoP_dataset28Aug20.xls") %>% rownames_to_column("ID") 

#Processing Demograpic data (Hobbies)

df_hobby <-df %>% select(Hobbies) 
df_hobby$Hobbies<- gsub("\\(", "", df_hobby$Hobbies)
df_hobby$Hobbies<- gsub("\\)", "", df_hobby$Hobbies)
df_hobby2<-df_hobby %>% separate(Hobbies, c("Hobbies1", "Hobbies2", "Hobbies3", "Hobbies4", "Hobbies5", "Hobbies6", "Hobbies7", "Hobbies8"), sep=",") %>%
  gather(Hobbies1:Hobbies8, key=Category, value=Hobbies) %>% select (-Category ) %>%
  na.omit(df_hobby)

#Weighting Criteria
df_weight <- df %>% select(PW1:PW28) %>% gather(key=Comparison, value=Trait) %>% filter(Trait !="Same") %>% na.omit() %>% group_by(Trait) %>% summarise (count=n()) 
df_maxcount <- df_weight %>% summarise(maximum=max(count)) 
df_weight <-  df_weight %>% mutate(weight=(count/df_maxcount$maximum)) %>% as.data.frame()

#Scoring respondant data        
df_scores <- df %>%   
        mutate_at(vars(P_AN5:P_RE4), likertNum)

#Summary scores for personality
df_scored <- df_scores %>% dplyr::group_by(ID) %>% 
  mutate(Anxiety = (sum(P_AN1, P_AN2, P_AN3, P_AN4, P_AN5 ) ) ,
                Social_Astuteness = (sum(P_AS1, P_AS2, P_AS3, P_AS4, P_AS5	)),
                Breadth_of_Interest = (sum(P_BR1, P_BR2, P_BR3, P_BR4, P_BR5	) ) ,
                Complexity = (sum(P_CM1, P_CM2, P_CM3, P_CM4, P_CM5) ) ,
                Social_Confidence = (sum(P_CD1, P_CD2, P_CD3, P_CD4, P_CD5) ) ,
                Cooperativeness = (sum(P_CO1, P_CO2, P_CO3, P_CO4, P_CO5)),
                Empathy = (sum(P_EM1, P_EM2, P_EM3, P_EM4, P_EM5) ) , 
                Energy_Level = (sum(P_EN1, P_EN2, P_EN3, P_EN4, P_EN5)) ,
                Innovation = (sum(P_IN1, P_IN2, P_IN3, P_IN4, P_IN5) ) , 
                Organization = (sum(P_OR1, P_OR2, P_OR3, P_OR4, P_OR5 ) ) , 
                Responsibility = (sum(P_RE1, P_RE2, P_RE3, P_RE4, P_RE5) ) ,
                Risk_Taking = (sum(P_RI1, P_RI2, P_RI3, P_RI4, P_RI5	) ) , 
                Sociability = (sum(P_SO1, P_SO2, P_SO3, P_SO4, P_SO5 ) ) , 
                Tolerance = (sum(P_TO1, P_TO2, P_TO3, P_TO4, P_TO5 ) ) ,
                Traditional_Values= (sum(P_TR1, P_TR2, P_TR3, P_TR4, P_TR5) )) %>% 
  select(ID, Group, Name, Anxiety:Traditional_Values, Email)

df_scored <- as.data.frame(df_scored)

#Scale socres to ES sample (n=151)
df_scored2 <- df_scored %>%
  group_by(ID) %>%
  mutate(Anxiety= (Anxiety-anxiety$Score) / anxiety$sd)   %>% 
  mutate(Breadth_of_Interest= (Breadth_of_Interest-breadth_of_interest$Score)/breadth_of_interest$sd)  %>% 
  mutate(Complexity= (Complexity - complexity$Score)/ complexity$sd)  %>% 
  mutate(Cooperativeness= (Cooperativeness-cooperativeness$Score)/cooperativeness$sd)  %>% 
  mutate(Empathy= (Empathy-empathy$Score)/empathy$sd) %>% 
  mutate(Energy_Level= (Energy_Level-energy_level$Score)/energy_level$sd) %>% 
  mutate(Innovation= (Innovation-innovation$Score)/innovation$sd)  %>%
  mutate(Organization= (Organization-organization$Score)/organization$sd) %>% 
  mutate(Responsibility= (Responsibility-responsibility$Score)/responsibility$sd) %>% 
  mutate(Risk_Taking= (Risk_Taking-risk_taking$Score)/risk_taking$sd)  %>% 
  mutate(Sociability= (Sociability-sociability$Score)/sociability$sd) %>%
  mutate(Social_Astuteness= (Social_Astuteness-social_astuteness$Score)/social_astuteness$sd) %>%
  mutate(Social_Confidence= (Social_Confidence-social_confidence$Score)/social_confidence$sd)  %>%
  mutate(Tolerance= (Tolerance-tolerance$Score)/tolerance$sd) %>%
  mutate(Traditional_Values= (Traditional_Values-traditional_values$Score)/traditional_values$sd)

df_scored2 <- as.data.frame(df_scored2)

   
#Confirmatory Factor Analysis Function
cfafunction <- function(df_dimension, m3a) {
df_dimension <- data.frame(df_dimension, row.names=1)
df_dimension <- na.omit (df_dimension)
onefactoranalysis <- cfa(m3a, data=df_dimension, std.lv=TRUE) 
summary(onefactoranalysis, fit.measures=TRUE, standardized=TRUE)
}

#CFA_Empathy
df_empathy <- df_scores %>% select(ID, P_EM1, P_EM2, P_EM3, P_EM4, P_EM5)
m3a_empathy <- 'f =~ 	P_EM1 + P_EM2 + P_EM3 + P_EM4 + P_EM5  '
cfafunction(df_empathy, m3a_empathy)

#CFA_Anxiety
df_anxiety <- df_scores %>% select(ID, P_AN1, P_AN2, P_AN3, P_AN4, P_AN5)
m3a_anxiety <- 'f =~ 	P_AN1 + P_AN2 + P_AN3 + P_AN4 + P_AN5  '
cfafunction(df_anxiety, m3a_anxiety)

#CFA_Risk
df_risk <- df_scores %>% select(ID, P_RI1, P_RI2, P_RI3, P_RI4, P_RI5)
m3a_risk <- 'f =~ 	P_RI1 + P_RI2 + P_RI3 + P_RI4 + P_RI5  '
cfafunction(df_risk, m3a_risk)

#CFA_Innovation
df_innovation <- df_scores %>% select(ID, P_IN1, P_IN2, P_IN3, P_IN4, P_IN5)
m3a_innovation <- 'f =~ 	P_IN1 + P_IN2 + P_IN3 + P_IN4 + P_IN5  '
cfafunction(df_innovation, m3a_innovation)
```
## Purpose  
Review a methodology for personality scale development  and showcase features of R statistical program  language and  R Markdown.  

This session follows the "IPIP Scale Construction Procedures" available at: https://ipip.ori.org/newScaleConstruction.htm .

<div class="blue">Hypothesis to test during this Session:  The Social Science "fit" of members of this CoP is similar to those performing other roles for Northrop Grumman. </div>

<div class="notes">
Empirical evidence is required to "to reject the null" and conclude that Social Scientists have a distinguishing personality profile.  
</div>

## Personality Assessment Overview
This 75 question personality assessment you completed aims to measure 15 underlying personality traits.  Measurements are similar to the <a href="https://w8y7a2j5.stackpathcdn.com/wp-content/uploads/2015/03/JPI-R-Scales.pdf">Jackson Personality Inventory - Revised (JPI-R)</a>.  

This ***JPI-R proxy*** consists of questions drawn from the public domain repository of personality questions  (https://ipip.ori.org/). <br>

## JPI-R Personality Dimensions

<div class="columns-2">
***Analytical Scales***

- Complexity 
- Breadth of Interest
- Innovation
- Tolerance

***Extroverted Scales***

- Sociability 
- Social Confidence 
- Energy Level

***Emotional*** 

- Empathy 
- Anxiety 
- Cooperativeness 

***Opportunistic*** 

- Risk Taking 
- Social Astuteness 

***Dependable***

- Organization 
- Traditional Values 
- Responsibility
</div>

<div class="notes">
- Complexity: seeks intricate solutions to problems
- Tolerance: accepts people even though they may differ from oneself; welcomes dissent
- Cooperativeness: is susceptible to social influence and group pressures; follows suit
- Social Astuteness: skillful at persuading others to achieve a particular goal; occasionally seen as manipulative of others
- Traditional Values: values traditional customs and beliefs; others may view individual as "old-fashioned"
- Responsibility: strong obligation to be honest and upright; an inflexibly conscience
</div>

## Scale Construction Process (1 of 2)

1. Correlate IPIP items (3,000) to 15 JPI-R dimensions and rank order IPIP items based on correlations. https://ipip.ori.org/ 
2. Inspect the highest positively correlated items for: alignment to intent of the JPI-R measurement and redundancy to other top questions. https://github.com/mattdeloia/JPIR_Analysis
3. Select the best five questions that tell a coherent story and perform reliability analysis of the items (confirmatory factor analysis using lavaan package in R).
4. Repeat question selection until achievement of a good fit model (TLI > 0.9).

*Data from ~400 individuals, JPI-R raw scores and IPIP question responses, are available in the Eugene-Springfield dataset. https://dataverse.harvard.edu/dataverse/ESCS-Data.

## Scale Construction Process (2 of 2)
<div class="columns-2">
***Anxiety Items***

- P_EM1	Am passionate about bettering the world's condition
- P_EM2	Often do nice things for people
- P_EM3	Know how to comfort others
- P_EM4	Am sensitive to the needs of others
- P_EM5	Am deeply moved by others' misfortunes

***Innovation Items***

- P_IN1	Come up with bold plans
- P_IN2	Am full of ideas
- P_IN3	Am an original thinker
- P_IN4	Have an imagination that stretches beyond that of my friends
- P_IN5	Love to think up new ways of doing things
</div>

<div class="notes">
Confirmatory factor analysis helps decide how well the data fits the model.  

Informs revisions revisions following scale construction and data collection.
</div>

```{r Confirmatory Factor Analysis, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#CFA_Anxiety
df_anxiety <- df_scores %>% select(ID, P_AN1, P_AN2, P_AN3, P_AN4, P_AN5)
m3a_anxiety <- 'f =~ 	P_AN1 + P_AN2 + P_AN3 + P_AN4 + P_AN5  '
cfafunction(df_anxiety, m3a_anxiety)

#CFA_Innovation
df_innovation <- df_scores %>% select(ID, P_IN1, P_IN2, P_IN3, P_IN4, P_IN5)
m3a_innovation <- 'f =~ 	P_IN1 + P_IN2 + P_IN3 + P_IN4 + P_IN5  '
cfafunction(df_innovation, m3a_innovation)
```

## CoP Personality Results (1 of 2)

```{r ScaledScores, echo=FALSE, message=FALSE, warning=FALSE}

personality_results2 <- df_scored2 %>% filter(Group=="SocialScience") %>% 
  gather(Anxiety:Traditional_Values, key=Dimension, value = Score) %>% group_by(Dimension) %>% 
  arrange(Dimension, ID) %>%  mutate(Average = movavg(Score, 8, type="s"))

personality_results2$ID <- as.integer(personality_results2$ID)

q <- personality_results2 %>%     
        ggplot(aes(x=reorder(Dimension, Average, FUN=mean), y=round(Average, 2), color=Dimension)) + 
        geom_point(size=3) +
        coord_flip() + ylim(-2.5,2.5) +
        geom_hline(yintercept=0, linetype="dotted") +
        xlab("") +
     ylab("moving average (z score)") +
        theme(legend.title= element_text(color="black", size=10), legend.position = "blank") 
 
  anim2 <- q + transition_time(ID) +  labs(title = "ID {frame_time}") + shadow_wake(wake_length = 0.1, alpha = FALSE)
animate(anim2, height=500, width=600)
```

## CoP Personality Results (2 of 2)

<div class="notes">
What aspects of personality are most stable or like the general workforce?
</div>

```{r PersonalityResults, echo=FALSE, message=FALSE, warning=FALSE}
personality_results <- df_scored2  %>% filter(Group=="SocialScience") %>% 
  gather(Anxiety:Traditional_Values, key=Dimension, value = Score) %>%
  summarySE(measurevar = "Score", groupvars = "Dimension") %>%
   mutate(Comparison = if_else(Score<=-.5, "Low", if_else(Score>=.5, "High", "Average")))
personality_results$Comparison <- factor (personality_results$Comparison, levels = c("High", "Average", "Low"))

personality_results %>% 
        mutate(Dimension=reorder(Dimension, Score, FUN=max)) %>%    
        ggplot(aes(x=Dimension, y=round(Score, 2), color=Comparison)) + 
        geom_point() +
        geom_errorbar(aes(ymin=Score-ci, ymax=Score+ci), width=.1 ) +
        coord_flip() + ylim(-2.5,2.5) +
        geom_hline(yintercept=0, linetype="dotted") +
        xlab("") +
     ylab("group mean with 95% ci (z score)") +
        scale_color_manual(name="general workforce comparison", values=c("green", "darkgray", "blue")) +
  theme(legend.title= element_text(color="black", size=10), legend.position = "top") + 
  labs(caption = "Note: z scores developed from ES Sample data (n~400)")
```

## CoP Analysis | Hierarchical Clustering Dendrogram

```{r HClustering, echo=FALSE, warning=FALSE}
clustering <- df_scores  %>% filter(Group=="SocialScience") %>% 
     select(P_AN5:P_RE4, Name) %>% column_to_rownames ("Name")
h_cluster <- hclust(dist(clustering))
h_cluster %>% ggdendrogram(rotate=TRUE, theme_dendro = TRUE, size=1)
```


## Value Modeling (1 of 3) | Evaluate Candidate Solutions

- Define Objective -> social science "Fit"
- Value Measures -> 8 latent traits selected among the 15 personality dimensions assessed
- Weights -> weights assigned to measures that reflect importance and range of scale
- Score -> raw scores determined from the personality assessment results (0 - 20)
- Value function -> function that assigns value to the score (ex. S curve, linear)
- Overall Score -> summation of ***weights x values*** across all measures

## Value Modeling (2 of 3)

8 of 15 traits were chosen to determine social science "fit"; experts rated importance of personality traits using AHP.

```{r Weightings, echo=FALSE, message=FALSE}
df_weight %>% ggplot(aes(x=reorder(Trait, weight, FUN=max), y=round(weight,2), label=round(weight,2))) + geom_col (fill="skyblue") + coord_flip() + geom_text () + xlab("") + ylab("Trait Weighting")
```

## Value Modeling (3 of 3)

Value model with ***value measures*** and ***weights*** displayed below.
```{r Model, echo=FALSE, message=FALSE}
branches <- as.data.frame(matrix(ncol=3, nrow = 8))
names(branches) <- c("Level1",  "leaves", "weights")
branches[1,] <- rbind("SocialScienceFit", "Responsibility", "1.00")
branches[2,] <- rbind("SocialScienceFit", "Energy", "1.00")
branches[3,] <- rbind("SocialScienceFit", "Complexity", "0.92")
branches[4,] <- rbind("SocialScienceFit", "Organization", "0.81")
branches[5,] <- rbind("SocialScienceFit", "Confidence", "0.81")
branches[6,] <- rbind("SocialScienceFit", "Tolerance", "0.73")
branches[7,] <- rbind("SocialScienceFit", "Empathy", "0.58")
branches[8,] <- rbind("SocialScienceFit", "Cooperativeness (R)", "0.46")
value_hierarchy_tree(branches$Level1,leaves=branches$leaves, weights=branches$weights, nodefillcolor="lightblue", leavesfillcolor = "green", leavesfontcolor = "black")
```

## Results (1 of 2)

```{r FitScores, echo=FALSE, message=FALSE}
df_fitscore   <- df_scored %>% 
  mutate(Cooperativeness=(26-Cooperativeness)) %>%
  gather(Anxiety:Traditional_Values, key=Trait, value=RawScore) %>%
  select(ID, Group, Trait, RawScore)

df_fitscore2 <- df_fitscore %>% left_join (df_weight, by = "Trait") %>%
  na.omit() %>% 
  mutate(WeightedScore = (RawScore*weight)) %>% 
  group_by(ID, Group) %>% 
  summarise(FitScore=sum(WeightedScore)) %>% as.data.frame() %>% mutate_at(vars(FitScore), scale)

df_fitscore2 %>% ggplot() + 
  geom_density(aes(x=FitScore, fill=Group), alpha=.7) +
  scale_fill_manual (values= c("gray", "skyblue"))
```

## Results (2 of 2)

<div class="notes">
Hypothesis to test during this Session:  The Social Science "fit" of members of this CoP is similar to those performing other roles for Northrop Grumman. 

Do you ***accept*** or ***reject*** this null hypothesis?
</div>

```{r FitScores2, echo=FALSE, message=FALSE, warning=FALSE}
df_fitscore2 %>% ggplot(aes(x=Group, y=FitScore, fill=Group)) + 
  geom_boxplot() +
  scale_fill_manual (values= c("gray", "skyblue")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "median", geom="text", size=3, color="red", vjust=-.5)
```

## Alternative Approach (Profile Analysis)
6 traits chosen to determine "fit." These traits suggest a unique personality profile due to differences from the ES sample.

```{r Model2, echo=FALSE, message=FALSE}
branchesb <- as.data.frame(matrix(ncol=3, nrow = 6))
names(branchesb) <- c("Level1",  "leaves", "weights")
branchesb[1,] <- rbind("SocialScienceFit", "Risk_Taking", "1.00")
branchesb[2,] <- rbind("SocialScienceFit", "Tolerance", "1.00")
branchesb[3,] <- rbind("SocialScienceFit", "Innovation", "1.00")
branchesb[4,] <- rbind("SocialScienceFit", "Breadth_of_Interest", "1.00")
branchesb[5,] <- rbind("SocialScienceFit", "Anxiety (R)", "1.00")
branchesb[6,] <- rbind("SocialScienceFit", "Cooperativeness (R)", "1.00")
value_hierarchy_tree(branchesb$Level1,leaves=branchesb$leaves, weights=branchesb$weights, nodefillcolor="lightblue", leavesfillcolor = "green", leavesfontcolor = "black")
```

## Alternative Approach Results

```{r FitScores3, echo=FALSE, message=FALSE, warning=FALSE}
df_fitscore3   <- df_scored %>% select(ID, Group, Risk_Taking, Tolerance, Innovation, Breadth_of_Interest, Anxiety, Cooperativeness) %>% mutate(Cooperativeness=(30-Cooperativeness), Anxiety=(30-Anxiety)) %>%
  gather(Risk_Taking:Cooperativeness, key=Trait, value=RawScore) %>%
  select(ID, Group, Trait, RawScore)  %>% 
  group_by(ID, Group) %>% 
  summarise(FitScore=sum(RawScore)) %>% as.data.frame() %>% mutate_at(vars(FitScore), scale)

df_fitscore3 %>% ggplot(aes(x=Group, y=FitScore, fill=Group)) + 
  geom_boxplot() +
  scale_fill_manual (values= c("gray", "skyblue")) +
  stat_summary(aes(label=round(..y..,2)), fun.y = "median", geom="text", size=3, color="red", vjust=-.5)
```
<div class="notes">
Hypothesis to test during this Session:  The Social Science "fit" of members of this CoP is similar to those performing other roles for Northrop Grumman. 

Do you ***accept*** or ***reject*** this null hypothesis?
</div>

## Hobbies Word Cloud 

```{r Hobbies, message=FALSE, warning=FALSE, echo=FALSE}
text2 <- df_hobby2$Hobbies# Create a corpus  
docs2 <- Corpus(VectorSource(text2))
docs2 <- docs2 %>%
  #tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
docs2 <- tm_map(docs2, content_transformer(tolower))
docs2 <- tm_map(docs2, removeWords, stopwords("english"))
dtm2 <- TermDocumentMatrix(docs2) 
matrix2 <- as.matrix(dtm2) 
words2 <- sort(rowSums(matrix2),decreasing=TRUE) 
df_text2 <- data.frame(word = names(words2),freq=words2)
wordcloud2(data=df_text2, size=.4, color='random-dark', backgroundColor = "lightgray" )
```

## References {data-background="Picture1.png" data-background-size=cover} 

Decision Making in Systems Engineering and Management (2nd ed.) edited by Gregory S. Parnell (Chapter 10, Problem Definition)

IPIP Scale Construction Procedures available at: https://ipip.ori.org/newScaleConstruction.htm .



## Back-Up: Trait Descriptions (1 of 3) 

Analytical <br>

 - Complexity: seeks intricate solutions to problems
 - Breadth of Interest: interested in learning about a diversity of things
 - Innovation: motivated to develop novel solutions to problems; values new ideas
 - Tolerance: accepts people even though they may differ from oneself; welcomes dissent

## Back-Up: Trait Descriptions (2 of 3) 
Emotional 

 - Empathy: tends to identify closely with other people and their problems
 - Anxiety: tends to worry over inconsequential matters; apprehensive about the future
 - Cooperativeness: is susceptible to social influence and group pressures; follows suit

Extroversion 

- Sociability: eagerly join a variety of social groups; actively social
- Social Confidence: confident in dealing with others; shows presence in interpersonal situations
- Energy level: is active and spirited; does not tire easily; capable of intense work for long periods

## Back-Up: Trait Descriptions (3 of 3) 
Opportunistic 

- Social Astuteness: skillful at persuading others to achieve a particular goal; occasionally seen as manipulative of others, but ordinarily diplomatic
- Risk Taking: enjoys gambling and taking a chance; willingly exposes self to situations with uncertain outcomes

Dependable 

- Organization: makes effective use of time; not easily distracted
- Traditional Values: values traditional customs and beliefs; others may view individual as "old-fashioned"
- Responsibility: strong obligation to be honest and upright; an inflexibly conscience   